Untitled

### 2023-08-12 draft_v0.Rmd
More exploring of times. From Windows.

# top 3 by month

@@

# START HERE

@@

@@

dta_um %>% 
  group_by(is.na(completion_timestamp)) %>% 
  count(name = "Nr_missing") %>% 
  ungroup() %>% 
  rename(Missing_completion_time = 1) %>% 
  mutate(across(Missing_completion_time, ~ifelse(.x == TRUE, "yes", "no")),
         Percentage = round(Nr_missing/x*100, 2)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

@@

# exclude data with no completion time

dta_um <- dta_um %>% 
  filter(!is.na(completion_timestamp))

@@

plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){

@@

>>>>

# top 10 by month

@@

# looks like parklands, milnerton, table view, marconi beam

# if look at median across months
dta_um %>% 
  group_by(month_creation, official_suburb) %>% 
  count() %>% 
  ungroup() %>% 
  group_by(official_suburb) %>% 
  summarise(med = median(n)) %>% 
  ungroup() %>% 
  arrange(desc(med))

x <- c("PARKLANDS", "MARCONI BEAM", "BRACKENFELL COMMON",
       "TABLE VIEW", "MILNERTON")

dta_um %>% 
  filter(official_suburb %in% x) %>% 
  group_by(official_suburb, code) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(aes(n, code, fill = official_suburb))+
  geom_col(position = "dodge")

@@

```{r}
# get back no fault found etc.

@@

dta_um %>% 
  group_by(is.na(completion_timestamp)) %>% 
  count(name = "Nr") %>% 
  ungroup() %>% 
  rename(Missing_completion_time = 1) %>% 
  mutate(across(Missing_completion_time, ~ifelse(.x == TRUE, "yes", "no")),
         Percentage = round(Nr/x*100, 2)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

@@

# exclude data with no completion time, create diff var

dta_um <- dta_um %>% 
  filter(!is.na(completion_timestamp)) %>% 
   mutate(time_hrs = as.integer(completion_timestamp - creation_timestamp)/60)

```{r}
#  create table withs medians, q80 for all suburbs and for all of city

time_tables_make <- function(dataset = dta_um, time_cutoff = NULL){

  if(is.null(time_cutoff)){

  tabledta <- dataset %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

  return(tabledta)

} else if(!is.null(time_cutoff)){

  dataset_x <- dataset %>% 
    filter(time_hrs < time_cutoff)

  tabledta_below <- dataset_x %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

  dataset_x <- dataset %>% 
    filter(time_hrs >= time_cutoff)

  tabledta_above <- dataset_x %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

  return(list(tabledta_below = tabledta_below,
                tabledta_above = tabledta_above))
}
}

time_dta_list <- list()

# for all of city, all codes, all completion time lengths

time_dta_list$all_times <- time_tables_make(dataset = dta_um, time_cutoff = NULL)

# for all of city, all codes, split by times < or > 96hrs
tmp <- time_tables_make(dataset = dta_um, time_cutoff = 96)

time_dta_list$below_96 <- tmp$tabledta_below 
time_dta_list$above_eq_96 <- tmp$tabledta_above

# weekends, public holidays?

@@

# START HERE
plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){

@@

  dataset %>% 
    mutate(col_select = "all_combined") %>% 
    group_by(col_select) %>% 
  summarise(n = n(),
            med_hrs = median(diff_time_hrs),
            q5 = quantile(diff_time_hrs, probs = 0.05),
            q80 = quantile(diff_time_hrs, probs = 0.8),
            q95 = quantile(diff_time_hrs, probs = 0.95)) %>% 
  ungroup()
